\vskip 0.2in
I am obliged to conduct my master program as a student of Quaid-I-Azam university, Islamabad. There were many experienced physicists around me and I could get their help and advice whenever I wanted. I was able to extend and develop my knowledge about high energy physics by the assistance from these people.
\newline
First of all I wish to express my sincere appreciation to my supervisor, Dr. Shamona Fawad Qazi, she convincingly guided and encouraged me to be professional even when things got difficult. Without her persistent help, the goal of this research work could not have been concluded.
\newline
I am extremely thankful to my instructor and co-supervisor, Dr. M. Bilal Kiani. He has always been supportive during the entire period of my master research work. Dr. Kiani has provided me with valuable discussions and advice. He introduced me to CMSSW, CMS offline software and how it operates, new to a novice like me. He has spent enormous time in teaching me and discussing data analysis with me.
\newline
The physical and technical contribution of ‘National Center for Physics (NCP), Islamabad’ is truly appreciated. Without their support and funding, my research work could not have reached its goal.
\newline
Now I have to thank my family, especially my parents. They were always very supportive and foundation behind this strenuous period.
\newline 
I am sincerely thankful to my senior Iqra and junior Sumaira. A constant support in this period.
\newline
I am also thankful to my research mates Jamshed, Sajid and Sunila for their insights and inputs whenever i got stuck on a problem.
\newline
There are still many more people I have to thank Afroze, Aiman, Arfa, Azkah, Esha, Hurriyat, Rafia, Mariyam (for the headphones), Mishal, Sana and Sephora. I am grateful to all of those colleagues who helped me directly or indirectly, in any way during this period.